
Run this to enable the rest of the program to run
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)

mcu <- read.csv('mcu dataset.csv')
View(data)
```
Hypthosesis Questions:
Hypothesis:Robert Downy Jr. has the highest average gross profit of gross - budget?
True
Hypothesis:Captain america has the lowest average metascore?  check
flase
Hypothesis:What movie has the highest total profit gross - budget? 
endgame
Hypothesis:What movie has the best meta score to budget-ratio?, check
Iron man
Hypothesis:What cast member is the least number of movies pointless 
many only have 1
Hypothesis:What movie made the most money after its release total gross - opening, check
endgame
Hypothesis: What director has the highest average metascore: check
IMDB.rating James Gunn, metacore of Ryan Coogler
Hypothesis: What actor has the highest average meta score/IMDB.rating? check
Chadwick Boseman, Tom Holland 

Hypothesis: Robert Downey Jr. Hast the most number of movies.check

Hyptothesis: What cast member has the highest average metascore.cheeck
Chadwick Boseman
Hyptothesis: What cast member has the highest average IMDBD rating check
Josh Brolin
Hypothesis: What is the average meta score for all the movies: check
The meta score avereage rating is  68.65217391304348

The average IMDB Rating has an average score of 7.4434782608695675 check

Hypothesis: What cast member is in the most movies. check
Rober Downey Jr.
Hypothesis: For each cast member what is the total number of the total gross check
Robert Downey J.

```{r}
mean(mcu$IMDB.rating)
```
```{r}
mean(mcu$metascore)
```

```{r}
# Assuming mcu is your data frame in R

# Replace dollar signs with an empty string
mcu$Budgetint <- gsub("\\$", "", mcu$Budget)

# Replace commas with an empty string
mcu$Budgetint <- gsub(",", "", mcu$Budgetint)

# Convert the column to numeric
mcu$Budgetint <- as.numeric(mcu$Budgetint)

#replace the dollar signs with an empty string
mcu$Total.Grossint <- gsub("\\$", "", mcu$Total.Gross)

#replace commas with an empty string
mcu$Total.Grossint <- gsub(",", "", mcu$Total.Grossint)

#convert the column to numeric
mcu$Total.Grossint <- as.numeric(mcu$Total.Grossint)

mcu$total_profit <- mcu$Total.Grossint - mcu$Budgetint


# Assuming your data frame is named 'mcu'
# You can replace these with your actual data frame and column names

max_row <- which.max(mcu$total_profit)
max_name <- mcu$Name[max_row]
max_value <- max(mcu$total_profit)

cat("The name with the maximum total profit is:", max_name, "\n")
cat("The maximum total profit is:", max_value, "\n")

```

What movie has the highest review to budget ratio to determine effienceny
```{r}

# Assuming mcu is your data frame in R

# Replace dollar signs with an empty string
mcu$Budgetint <- gsub("\\$", "", mcu$Budget)

# Replace commas with an empty string
mcu$Budgetint <- gsub(",", "", mcu$Budgetint)

# Convert the column to numeric
mcu$Budgetint <- as.numeric(mcu$Budgetint)

mcu$Review_to_Buget <- mcu$metascore/mcu$Budgetint

max_row <- which.max(mcu$Review_to_Buget)
max_name <- mcu$Name[max_row]
max_value <- max(mcu$Review_to_Buget)

cat("The name with the maximum total profit is:", max_name, "\n")
cat("The maximum total profit is:", max_value, "\n")


```
Does Captain america has the lowest average metascore?
```{r}
captain_america <- subset(mcu, grepl("Chris Evans", Cast))
mean(captain_america$metascore)
hulk <- subset(mcu, grepl("Edward Norton", Cast))
mean(hulk$metascore)
```
Captain america does not have the lowest metascore

What director has the highest average metascore?

```{r}
Directors <- c('Jon Favreau', 'Louis Leterrier', 'Kenneth Branagh', 'Joe Jhonston', 'Joss Whedon', 'Shane Black', 
             'Alan Taylor', 'Anthony and Joe Russo','James Gunn' ,'Peyton Reed', 'Scott Derrickson', 'Jon Watts', 
             'Ryan Coogler', 'Anna Boden and Ryan Fleck')

for (director in Directors) { 
average_director <- subset(mcu, grepl(director, Director))
cat("The Director has the average score of",director,mean(average_director$metascore),"\n")
}
```
Ryan Coogler has the highest meta score of 88

```{r}
Directors <- c('Jon Favreau', 'Louis Leterrier', 'Kenneth Branagh', 'Joe Jhonston', 'Joss Whedon', 'Shane Black', 
             'Alan Taylor', 'Anthony and Joe Russo','James Gunn' ,'Peyton Reed', 'Scott Derrickson', 'Jon Watts', 
             'Ryan Coogler', 'Anna Boden and Ryan Fleck')

for (director in Directors) { 
average_director <- subset(mcu, grepl(director, Director))
cat("The Director has the average score of",director,mean(average_director$IMDB.rating),"\n")
}
```
The director james gunn has the highest IMDB rating

```{r}
casts <- c(
    "Robert Downey Jr.",
    'Gweneth Paltrow ',
    'Terrence Howard',
    'Edward Norton',
    'Liv Tyler',
    'Tim Roth',
    'Mickey Rourke',
    'Chris Hemsworth',
    'Anthony Hopkins',
    'Natalie Portman',
    'Chris Evans',
    'Hugo Weaving',
    'Samuel L. Jackson',
    'Scarlett Johansson',
    'Jeremy Renner',
    'Guy Pearce',
    'Tom Hiddleston',
    'Chris Patt', 
    'Vin Diesel',
    'Bradely Cooper',
    'Mark Ruffalo',
    'Paul Rudd',
    'Michael Douglas',
    'Corey Stall',
    'Sebastian Stan',
    'Benedict Cumberbatch',
    'Chiswetel Ejiofor',
    'Racheal McAdams',
    'Zoe Saldana',
    'Dave Bautista',
    'Michael Keaton',
    'Cate Blanchett',
    'Chadwick Boseman',
    'Michael B. Jordan',
    "Josh Brolin",
    "Jake Gyllenhaal",
    "Lupita Nyong'o"
)
char <- ''
max <- 0
min <- 100
charmin<-''
for (cast in casts) { 
average_cast <- subset(mcu, grepl(cast, Cast))
if(mean(average_cast$metascore) > max){
  char <- cast
  max <- mean(average_cast$metascore)
}

if(mean(average_cast$metascore) < min){
  charmin <- cast
  min <- mean(average_cast$metascore)
}
cat("The actor member has the average metascore of",cast,mean(average_cast$metascore),"\n")
}
cat("The actor with the hightest metascore is ", char, max,"\n")
cat("The actor with the lowest metascore is ", charmin, min)
```

```{r}
casts <- c(
    "Robert Downey Jr.",
    'Gweneth Paltrow ',
    'Terrence Howard',
    'Edward Norton',
    'Liv Tyler',
    'Tim Roth',
    'Mickey Rourke',
    'Chris Hemsworth',
    'Anthony Hopkins',
    'Natalie Portman',
    'Chris Evans',
    'Hugo Weaving',
    'Samuel L. Jackson',
    'Scarlett Johansson',
    'Jeremy Renner',
    'Guy Pearce',
    'Tom Hiddleston',
    'Chris Patt', 
    'Vin Diesel',
    'Bradely Cooper',
    'Mark Ruffalo',
    'Paul Rudd',
    'Michael Douglas',
    'Corey Stall',
    'Sebastian Stan',
    'Benedict Cumberbatch',
    'Chiswetel Ejiofor',
    'Racheal McAdams',
    'Zoe Saldana',
    'Dave Bautista',
    'Michael Keaton',
    'Cate Blanchett',
    'Chadwick Boseman',
    'Michael B. Jordan',
    "Josh Brolin",
    "Jake Gyllenhaal",
    "Lupita Nyong'o"
)
char <- ''
max <- 0
for (cast in casts) { 
average_cast <- subset(mcu, grepl(cast, Cast))
if(mean(average_cast$IMDB.rating) > max){
  char <- cast
  max <- mean(average_cast$IMDB.rating)
}
cat("The Cast member has the average score of",cast,mean(average_cast$IMDB.rating),"\n")
}
cat("The lead actor with the hightest meta score is", char, max )
```

```{r}
casts <- c(
    "Robert Downey Jr.",
    'Gweneth Paltrow ',
    'Terrence Howard',
    'Edward Norton',
    'Liv Tyler',
    'Tim Roth',
    'Mickey Rourke',
    'Chris Hemsworth',
    'Anthony Hopkins',
    'Natalie Portman',
    'Chris Evans',
    'Hugo Weaving',
    'Samuel L. Jackson',
    'Scarlett Johansson',
    'Jeremy Renner',
    'Guy Pearce',
    'Tom Hiddleston',
    'Chris Patt', 
    'Vin Diesel',
    'Bradely Cooper',
    'Mark Ruffalo',
    'Paul Rudd',
    'Michael Douglas',
    'Corey Stall',
    'Sebastian Stan',
    'Benedict Cumberbatch',
    'Chiswetel Ejiofor',
    'Racheal McAdams',
    'Zoe Saldana',
    'Dave Bautista',
    'Michael Keaton',
    'Cate Blanchett',
    'Chadwick Boseman',
    'Michael B. Jordan',
    "Josh Brolin",
    "Jake Gyllenhaal",
    "Lupita Nyong'o"
)
char <- ''
max <- 0
for (cast in casts) { 
average_cast <- subset(mcu, grepl(cast, Cast))
cast_count = nrow(average_cast)
if(cast_count > max){
  char <- cast
  max <- cast_count
}
cat("The cast member has the count of movies",cast,cast_count,"\n")
}
cat("The cast with the hightest count is ", char, max )

```

```{r}
casts <- c(
    "Robert Downey Jr.",
    'Gweneth Paltrow ',
    'Terrence Howard',
    'Edward Norton',
    'Liv Tyler',
    'Tim Roth',
    'Mickey Rourke',
    'Chris Hemsworth',
    'Anthony Hopkins',
    'Natalie Portman',
    'Chris Evans',
    'Hugo Weaving',
    'Samuel L. Jackson',
    'Scarlett Johansson',
    'Jeremy Renner',
    'Guy Pearce',
    'Tom Hiddleston',
    'Chris Patt', 
    'Vin Diesel',
    'Bradely Cooper',
    'Mark Ruffalo',
    'Paul Rudd',
    'Michael Douglas',
    'Corey Stall',
    'Sebastian Stan',
    'Benedict Cumberbatch',
    'Chiswetel Ejiofor',
    'Racheal McAdams',
    'Zoe Saldana',
    'Dave Bautista',
    'Michael Keaton',
    'Cate Blanchett',
    'Chadwick Boseman',
    'Michael B. Jordan',
    "Josh Brolin",
    "Jake Gyllenhaal",
    "Lupita Nyong'o"
)

char <- ''
max <- 0

for (cast in casts) { 
    sum_total_gross <- subset(mcu, grepl(cast, Cast))
    if (sum(sum_total_gross$Total.Grossint, na.rm = TRUE) > max) {
        char <- cast
        max <- sum(sum_total_gross$Total.Grossint, na.rm = TRUE)
    }
    cat("The Cast member", cast, "has a total gross of", sum(sum_total_gross$Total.Grossint, na.rm = TRUE), "\n")
}

cat("The cast with the highest total gross is", char, "with a total gross of", max, "\n")

```
```{r}
casts <- c(
    "Robert Downey Jr.",
    'Gweneth Paltrow ',
    'Terrence Howard',
    'Edward Norton',
    'Liv Tyler',
    'Tim Roth',
    'Mickey Rourke',
    'Chris Hemsworth',
    'Anthony Hopkins',
    'Natalie Portman',
    'Chris Evans',
    'Hugo Weaving',
    'Samuel L. Jackson',
    'Scarlett Johansson',
    'Jeremy Renner',
    'Guy Pearce',
    'Tom Hiddleston',
    'Chris Patt', 
    'Vin Diesel',
    'Bradely Cooper',
    'Mark Ruffalo',
    'Paul Rudd',
    'Michael Douglas',
    'Corey Stall',
    'Sebastian Stan',
    'Benedict Cumberbatch',
    'Chiswetel Ejiofor',
    'Racheal McAdams',
    'Zoe Saldana',
    'Dave Bautista',
    'Michael Keaton',
    'Cate Blanchett',
    'Chadwick Boseman',
    'Michael B. Jordan',
    "Josh Brolin",
    "Jake Gyllenhaal",
    "Lupita Nyong'o"
)

char <- ''
max <- 0

for (cast in casts) { 
    sum_total_gross <- subset(mcu, grepl(cast, Cast))
    if (sum(sum_total_gross$Total.Grossint, na.rm = TRUE) - sum(sum_total_gross$Budgetint, na.rm = TRUE) > max) {
        char <- cast
        max <- sum(sum_total_gross$Total.Grossint, na.rm = TRUE)- sum(sum_total_gross$Budgetint, na.rm = TRUE)
    }
    cat("The Cast member", cast, "has a total gross of", sum(sum_total_gross$Total.Grossint, na.rm = TRUE) - sum(sum_total_gross$Budgetint, na.rm = TRUE), "\n")
}

cat("The cast with the highest total gross is", char, "with a total gross of", max, "\n")

```
```{r}
Directors <- c('Jon Favreau', 'Louis Leterrier', 'Kenneth Branagh', 'Joe Jhonston', 'Joss Whedon', 'Shane Black', 
             'Alan Taylor', 'Anthony and Joe Russo','James Gunn' ,'Peyton Reed', 'Scott Derrickson', 'Jon Watts', 
             'Ryan Coogler', 'Anna Boden and Ryan Fleck')
max <- 0
dir <- ''

for (director in Directors) { 
average_director <- subset(mcu, grepl(director, Director))
if (mean(average_director$Total.Grossint) > max) {
  dir <- director
  max <- mean(average_director$Total.Grossint)
  
}
cat("The Director has the average score of",director,mean(average_director$Total.Grossint),"\n")
}
cat("The Director has the highest average total gross of",dir,"of",max)
```




